---
title: "Regression Analysis of Bike Sharing Demand"
author: "Chance Robinson, Jayson Barker and Neha Dixit"
date: |
  Master of Science in Data Science, Southern Methodist University, USA
lang: en-US
class: man
figsintext: true
numbersections: true
encoding: UTF-8
bibliography: references.bib
biblio-style: apalike
output:
  bookdown::pdf_document2:
     citation_package: natbib
     keep_tex: true
     toc: false
header-includes:
   - \usepackage{amsmath}
   - \usepackage[utf8]{inputenc}
   - \usepackage[T1]{fontenc}
   - \usepackage{setspace}
   - \usepackage{hyperref}
   - \onehalfspacing
   - \setcitestyle{numbers,square,super}
   - \newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
editor_options: 
  chunk_output_type: console
---


```{r, lib-read, results='hide', message=FALSE, include=FALSE, echo=FALSE}
setwd('.')

# library imports
library(tidyverse)
# Date manipulation
library(lubridate)
# Plotting
library(olsrr)
# RMLSE
library(MLmetrics)
# Correlation Matrix
library(ggcorrplot)
# Lasso
library(glmnet)
# AIC commands
library(MASS)

```


```{r, load-data, results='hide', message=FALSE, include=FALSE, echo=FALSE}
# seed data
set.seed(12345)

# read from csv into test and train data sets
train <- read_csv('./data/train.csv')
test <- read_csv('./data/test.csv')

```



# Introduction

[Intro]


# Data Description

The dataset we chose for this project was a publicly shared, hourly bike sharing dataset made available through Kaggle in csv format. 

This data set is divided into two distinct sets – a train and test set. The train set consists of 10,886 rows (titled "train.csv") and the test set consists of 6,493 rows (titled "test.csv"). Within the training set, the first 19 days of each month are captured whereas in the test data set, the 20th day to the end of each month is present. The entirity of the data spans from 1/1/2011 through 12/31/2012 - encompassing two full years of bike sharing data. Interstingly, the time component of this analysis is captured in hours of each day meaning we have a calendar date represented 24 times (for each hour of that day) in the data, along with it's associated attribute values.

In train data set, there are a total of 12 attributes which capture multiple variables related to bike rentals. Some of these attributes are categorical, and others are continuous. All attributes are summarized in the table below:

  Column Name      |Type                  |Description
  -----------------|--------------------- |------------------------------------------------
  1.  datetime     |    Date			        |YYYY-MM-DD HH24 (example:  2011-01-01 04:00:00)
  2.  season       |    Integer 		      |(1-4)
  3.  holiday      |    Integer 		      |(0 or 1)
  4.  workingday   |    Integer 		      |(0 or 1)
  5.  weather      |    Integer 		      |(1-4)
  6.  temp         |    Float 			      |temparture in Celcius
  7.  atemp        |    Float 			      |"feels like" temperature in Celsius
  8.  humidity     |    Integer           |relative humidity
  9.  windspeed    |    Float             |wind speed
  10. casual       |    Integer 		      |count of casual users 
  11. registered   |    Integer 		      |count of registered users 
  12. count        |    Integer 		      |count of total users `response variable`
  

** The test data set lacks the casual, registered and count variables.


\newpage

# Exploratory Data Analysis

* Plotting Explanatory vs. Response Variables


```{r, categorical-factors, results='hide', message=FALSE, include=FALSE, echo=FALSE}

# copy the test and train data sets for EDA
train.mod.1 <- train
test.mod.1 <- test

train.mod.1$season <- factor(train.mod.1$season, labels = c("Spring", "Summer", "Fall", "Winter"))
test.mod.1$season <- factor(test.mod.1$season, labels = c("Spring", "Summer", "Fall", "Winter"))

table(train.mod.1$season)

train.mod.1$holiday <- factor(train.mod.1$holiday, labels = c("No", "Yes"))
test.mod.1$holiday <- factor(test.mod.1$holiday, labels = c("No", "Yes"))

table(train.mod.1$holiday)

train.mod.1$workingday <- factor(train.mod.1$workingday, labels = c("No", "Yes"))
test.mod.1$workingday <- factor(test.mod.1$workingday, labels = c("No", "Yes"))

table(train.mod.1$workingday)

train.mod.1$weather <- factor(train.mod.1$weather, labels = c("Great", "Good", "Average", "Poor"))
test.mod.1$weather <- factor(test.mod.1$weather, labels = c("Great", "Good", "Average", "Poor"))

table(train.mod.1$weather)


```



## Categorical Variables

Several numeric variables were found to be better suited to categorization and were converted to factors.

### Season

Season           |Label                 |Description
-----------------|--------------------- |------------------------------------------------
1                | Spring               | Dec 21 ~ Mar 20
2                | Summer               | Mar 21 ~ Jun 20
3                | Fall                 | Jun 21 ~ Sep 20
4                | Winter               | Sep 21 ~ Dec 20

```{r, train.mod.1.season, echo=FALSE}

train.mod.1 %>%
  ggplot(aes(x=season, y=count, fill=season)) + geom_boxplot()


```


\newpage

#### Holiday

```{r, train.mod.1.holiday, echo=FALSE}

train.mod.1 %>%
  ggplot(aes(x=holiday, y=count, fill=holiday)) + geom_boxplot()


```


### Working Day


```{r, train.mod.1.workingday, echo=FALSE}

train.mod.1 %>%
  ggplot(aes(x=workingday, y=count, fill=workingday)) + geom_boxplot()


```



\newpage

### Weather


```{r, train.mod.1.weather, echo=FALSE}

train.mod.1 %>%
  ggplot(aes(x=weather, y=count, fill=weather)) + geom_boxplot()


```


The datetime column was broken out into multiple factors as well so that we could visualize the components of each date and aggregate by different dimensions of the timestamp.  We felt this was also necessary due to the nature of how the train/ test data sets had been pre-split.  (i.e...with the first 19 days of the month holding the only true counts to validate our models against.)

* Year
* Month
* Day
* Hour


```{r, split-date, results='hide', message=FALSE, include=FALSE, echo=FALSE}

library(lubridate)

train.mod.1 <- train.mod.1 %>%
  mutate(year = as.factor(format(datetime, format = "%Y")), 
         month = as.numeric(format(datetime, format = "%m")), 
         day = as.factor(format(datetime, format = "%d")),
         hour = as.factor(format(datetime, format = "%H")))

test.mod.1 <- test.mod.1 %>%
  mutate(year = as.factor(format(datetime, format = "%Y")), 
         month = as.numeric(format(datetime, format = "%m")), 
         day = as.factor(format(datetime, format = "%d")),
         hour = as.factor(format(datetime, format = "%H")))


# train.mod.1
# test.mod.1

# Convert Months to Ordered Factor 
train.mod.1$month <-month(train.mod.1$datetime, label = TRUE, abbr = FALSE)
test.mod.1$month <-month(test.mod.1$datetime, label = TRUE, abbr = FALSE)

```


### Month

```{r, train.mod.1.month, echo=FALSE}

train.mod.1 %>%
  ggplot(aes(x=month, y=count, fill=month)) + geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


```



\newpage


## Continuous Variables

### Count by Temperature

```{r, train.mod.1.temp, echo=FALSE}

train.mod.1 %>%
  ggplot(aes(x = temp, y = count)) + 
  geom_point(alpha = 0.3) + 
  scale_x_continuous(breaks = seq(from = 0, to = 45, by = 2)) + 
  geom_smooth(method = 'lm')

```


\newpage

### Count by "Feels like" Temperature


```{r, train.mod.1.atemp, echo=FALSE}

train.mod.1 %>%
  ggplot(aes(x = atemp, y = count)) + 
  geom_point(alpha = 0.3) + 
  scale_x_continuous(breaks = seq(from = 0, to = 45, by = 2)) + 
  geom_smooth(method = 'lm')

```


\newpage

### Count by Wind Speed


```{r, train.mod.1.windspeed, echo=FALSE}

train.mod.1 %>%
  ggplot(aes(x = windspeed, y = count)) + 
  geom_point(alpha = 0.3) + 
  scale_x_continuous(breaks = seq(from = 0, to = 60, by=2)) + 
  geom_smooth(method = 'lm')

```



\newpage

## Correlation Matrix

There are several variables with a relatively high level of covariance from the training set.  The following columns should therefore be removed so as not to be picked up by any automated modelling techniques. 

* atemp
* causual 
* registered


```{r, train.mod.1.corr.matrix, echo=FALSE}

train.mod.1.numeric <- train.mod.1 %>%
  select_if(is.numeric)


corr <- round(cor(train.mod.1.numeric), 1)
  
ggcorrplot(corr, method = "circle")


train.mod.1$atemp <- NULL
train.mod.1$casual <- NULL
train.mod.1$registered <- NULL

# train.mod.1


```



\newpage

# Objective I Analysis


## Question of Interest


The team be utilizing the multiple linear regression techniques we've learned up to this point in the program to predict the bike rental deman on a given date and time.  The model will be evaluated on the Root Mean Squared Logarithmic Error, or RMSLE.  As this data represents hourly data collected, there is an obvious time component associated with this particular competition.  We wanted to gauge how effective mutiple linear regression would be when the assumption of indepdence is clearly violated.


```{r remove-outliers, echo=FALSE}

# log transform the response variable
train.mod.1$count <- log(train.mod.1$count)


train.mod.1 %>%
  group_by(month) %>%
  summarize(mean = mean(count), sd = sd(count), median = median(count), observations = n())


outliers <- train.mod.1[   train.mod.1$count < median(train.mod.1$count) - (sd(train.mod.1$count) * 3), ]


# remove outliers
train.mod.1 <- train.mod.1 %>%
  filter(!datetime %in% outliers$datetime)


train[5555, ] # 2012-01-09 18:00:00


train.mod.1 <- train.mod.1 %>%
  filter(datetime != '2012-01-09 18:00:00')



# train.mod.1  %>%
#   ggplot(aes(x=month, y=count, fill=month)) + geom_boxplot() + 
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))

```


## Model Selection

### Lasso


```{r}

split.perc = .80

train.indices = sample(1:dim(train.mod.1)[1],round(split.perc * dim(train.mod.1)[1]))

train.mod.1.train = train.mod.1[train.indices,]
train.mod.1.test  = train.mod.1[-train.indices,]


train.mod.1.train$datetime <- NULL
train.mod.1.test$datetime <- NULL


train.mod.1.train

x <- model.matrix(count~.,train.mod.1.train)[,-7]
y <- train.mod.1.train$count

grid=10^seq(10,-2, length =100)
lasso.model <- glmnet(x,y,alpha=1, lambda=grid)

xtest<-model.matrix(count~.,train.mod.1.test)[,-7]
ytest <- train.mod.1.test$count


cv.out=cv.glmnet(x,y,alpha=1) #alpha=1 performs LASSO
plot(cv.out)
best.lambda <-cv.out$lambda.min  #Optimal penalty parameter.  You can make this call visually.
lasso.pred=predict(lasso.model ,s=best.lambda ,newx=xtest)

testMSE_LASSO<-mean((ytest-lasso.pred)^2)
testMSE_LASSO


```


### Custom Variable Selection 

We developed the best fitting model with a custom selection of variables after having accounted for those with high correlation and adding interactive terms such as month/ hour based on the seasonal nature that the box plots exhibited.

```{r, custom-model, echo=FALSE}

custom.model.formula = count ~ weather + 
                             windspeed + 
                             temp + 
                             month +
                             hour +
                             month:hour


custom.model  <- lm(formula = custom.model.formula, data = train.mod.1)

par(mfrow=c(2,2))
plot(custom.model)

# summary(custom.model)

ols_plot_resid_lev(custom.model)

```

### RMSLE: Root Mean Squared Logarithmic Error Loss
```{r, cutom-rmsle, echo=FALSE}

RMSLE(y_pred = floor(ifelse(custom.model$fitted.values < 0, 0, custom.model$fitted.values)), y_true = train.mod.1$count)

```



### Stepwise

```{r, stepwise-model,echo=FALSE}

train.mod.1$datetime <- NULL
train.mod.1$datetime <- NULL

# Fit the model with all parameters
fit1 <- lm(count ~ ., data=train.mod.1)
# Fit the model with only 1 parameter
fit2 <- lm(count ~ 1, data=train.mod.1)


# stw.model <- stepAIC(fit2,direction="both",scope=list(upper=fit1,lower=fit2))
# summary(stw.model)

stw.model.formula <- count ~ hour + month + year + weather + temp + humidity + workingday + windspeed + holiday

stw.model <- lm(stw.model.formula,
               data = train.mod.1)

# summary(stw.model)

test$count <- predict.lm(stw.model, test.mod.1)
test$count <- exp(test$count)

# when less that 0, replace
test <- test %>%
  mutate(count = round(ifelse(count < 0, 0, count)))

head(test)

# submit <- test %>% subset(select=c(datetime, count))
# write.csv(submit, file = "./stepwise_kaggle_submission.csv", row.names = F)

```



\newpage


## Model Assumptions Assessment

* The response variable is linear
* The data is normally distributed
* Independence

## Comparing Competing Models






\newpage

## Parameters

[Parameters]

## Model Interpretation

[Model Interpretation]


## Conclusion

[Conclusion]

\newpage

# Objective II Analysis


## Question of Interest


[Discuss time series method]


**Time-Series Analysis**


[Details goe here]


## Model Assumption Assessment


[Model Assumption Assessment]


## Comparing Competing Models


## Conclusion


[Conclusion]


\newpage

# Appendix


## Code

\newpage

# References
