---
title: "Objective 2 Analysis"
author: "Chance Robinson"
date: "9/27/2019"
output: 
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Exploratory Data Analysis


### Library Imports

```{r libraries, quietely=TRUE, message = FALSE, echo = FALSE, warn.conflicts=FALSE}
library(tidyverse)
# Date manipulation
library(lubridate)
# RMLSE
library(MLmetrics)
# Time Series Analysis
library(tseries)
library(forecast)
```

### Load the csv data


```{r load, results='hide', message=FALSE}

train <- read_csv('../../../data/train.csv')
test <- read_csv('../../../data/test.csv')

```

### Data Dictionary

  Column Name      | 	Type                Description
  -----------------|    ----------------- | ------------------------------------------------
  1.  datetime     |    Date			        | YYYY-MM-DD HH24 (example:  2011-01-01 04:00:00)
  2.  season       |    Integer 		      |	(1-4)
  3.  holiday      |    Integer 		      |	(0 or 1)
  4.  workingday   |    Integer 		      |	(0 or 1)
  5.  weather      |    Integer 		      |	(1-4)
  6.  temp         |    Float 			      |	temparture in Celcius
  7.  atemp        |    Float 			      |	"feels like" temperature in Celsius
  8.  humidity     |    Integer           | relative humidity
  9.  windspeed    |    Float             | wind speed
  10. casual       |    Integer 		      |	count of casual users 
  11. registered   |    Integer 		      |	count of registered users 
  12. count        |    Integer 		      |	count of total users `response variable`
  
  
### Factors

  * season
    + 1 = Dec 21 ~ March 20 (Spring)
    + 2 = March 21 ~ Jun 20 (Summer)
    + 3 = June 21 ~ Sept 20 (Fall)
    + 4 = Sept 21 ~ Dec 20  (Winter)

  * holiday
    + 0 = No
    + 1 = Yes
    
  * workingday
    + 0 = No
    + 1 = Yes
    
```{r factors}
train$season <- factor(train$season, labels = c("Spring", "Summer", "Fall", "Winter"))
test$season <- factor(test$season, labels = c("Spring", "Summer", "Fall", "Winter"))

table(train$season)

train$holiday <- factor(train$holiday, labels = c("No", "Yes"))
test$holiday <- factor(test$holiday, labels = c("No", "Yes"))

table(train$holiday)

train$workingday <- factor(train$workingday, labels = c("No", "Yes"))
test$workingday <- factor(test$workingday, labels = c("No", "Yes"))

table(train$workingday)

train$weather <- factor(train$weather, labels = c("Great", "Good", "Average", "Poor"))
test$weather <- factor(test$weather, labels = c("Great", "Good", "Average", "Poor"))


# table(train$weather)


```



### Split Date-Time (Both)

- Year, Month, Day and Hour

```{r}

# library(lubridate)

train <- train %>%
  mutate(year = as.factor(format(datetime, format = "%Y")), 
         month = as.numeric(format(datetime, format = "%m")), 
         day = as.numeric(format(datetime, format = "%d")),
         hour = as.factor(format(datetime, format = "%H")))

test <- test %>%
  mutate(year = as.factor(format(datetime, format = "%Y")), 
         month = as.numeric(format(datetime, format = "%m")), 
         day = as.numeric(format(datetime, format = "%d")),
         hour = as.factor(format(datetime, format = "%H")))


```


### Convert Months to Ordered Factor (Both)

```{r}

train$month <-month(train$datetime, label = TRUE, abbr = FALSE)
test$month <-month(test$datetime, label = TRUE, abbr = FALSE)

# need to convert the datetime column to a string for rbind function
train$datetime <-as.character(train$datetime)
test$datetime <-as.character(test$datetime)

```



#### Modeling

    - psuedo code

    - Loop through years (train and test)

    - Loop through months (train and test)

    - fit AR model

    - Forcast x number of observations based on nrow from test dataframe and impute the count from the time series forecast
    

## 2011

### January


```{r}

train1 <- train %>%
  filter(year == '2011' & month == 'January') %>%
  select(datetime, count)

test1 <- test %>%
  filter(year == '2011' & month == 'January') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train1)
# head(test1)

AR24 <- arima(train1$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test1)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test1$count <- round(fcst$mean)
# test1

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train1$count)

```

### February

```{r}


train2 <- train %>%
  filter(year == '2011' & month == 'February') %>%
  select(datetime, count)

test2 <- test %>%
  filter(year == '2011' & month == 'February') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train2)
# head(test2)

AR24 <- arima(train2$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test2)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test2$count <- round(fcst$mean)


RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train2$count)


```


### March

```{r}


train3 <- train %>%
  filter(year == '2011' & month == 'March') %>%
  select(datetime, count)

test3 <- test %>%
  filter(year == '2011' & month == 'March') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train3)
# head(test3)

AR24 <- arima(train3$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test3)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test3$count <- round(fcst$mean)

# test3

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train3$count)

```


### April

```{r}


train4 <- train %>%
  filter(year == '2011' & month == 'April') %>%
  select(datetime, count)

test4 <- test %>%
  filter(year == '2011' & month == 'April') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train4)
# head(test4)

AR24 <- arima(train4$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test4)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test4$count <- round(fcst$mean)


RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train4$count)


```


### May

```{r}


train5 <- train %>%
  filter(year == '2011' & month == 'May') %>%
  select(datetime, count)

test5 <- test %>%
  filter(year == '2011' & month == 'May') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train5)
# head(test5)

AR24 <- arima(train5$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test5)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test5$count <- round(fcst$mean)

# test5

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train5$count)

```

### June

```{r}


train6 <- train %>%
  filter(year == '2011' & month == 'June') %>%
  select(datetime, count)

test6 <- test %>%
  filter(year == '2011' & month == 'June') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train6)
# head(test6)

AR24 <- arima(train6$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test6)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test6$count <- round(fcst$mean)

# test6

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train6$count)

```

### July

```{r}


train7 <- train %>%
  filter(year == '2011' & month == 'July') %>%
  select(datetime, count)

test7 <- test %>%
  filter(year == '2011' & month == 'July') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train7)
# head(test7)

AR24 <- arima(train7$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test7)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test7$count <- round(fcst$mean)

# test7

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train7$count)

```


### August

```{r}

train8 <- train %>%
  filter(year == '2011' & month == 'August') %>%
  select(datetime, count)

test8 <- test %>%
  filter(year == '2011' & month == 'August') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train8)
# head(test8)

AR24 <- arima(train8$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test8)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test8$count <- round(fcst$mean)

# test8

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train8$count)

```


### September

```{r}

train9 <- train %>%
  filter(year == '2011' & month == 'September') %>%
  select(datetime, count)

test9 <- test %>%
  filter(year == '2011' & month == 'September') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train9)
# head(test9)

AR24 <- arima(train9$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test9)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test9$count <- round(fcst$mean)

# test9

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train9$count)

```


### October

```{r}

train10 <- train %>%
  filter(year == '2011' & month == 'October') %>%
  select(datetime, count)

test10 <- test %>%
  filter(year == '2011' & month == 'October') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train10)
# head(test10)

AR24 <- arima(train10$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test10)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test10$count <- round(fcst$mean)

# test10

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train10$count)

```



### November

```{r}

train11 <- train %>%
  filter(year == '2011' & month == 'November') %>%
  select(datetime, count)

test11 <- test %>%
  filter(year == '2011' & month == 'November') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train11)
# head(test11)

AR24 <- arima(train11$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test11)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test11$count <- round(fcst$mean)

# test11

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train11$count)

```


### December

```{r}

train12 <- train %>%
  filter(year == '2011' & month == 'December') %>%
  select(datetime, count)

test12 <- test %>%
  filter(year == '2011' & month == 'December') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train12)
# head(test12)

AR24 <- arima(train12$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test12)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test12$count <- round(fcst$mean)

# test12

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train12$count)

```


## 2012

### January


```{r}

train13 <- train %>%
  filter(year == '2012' & month == 'January') %>%
  select(datetime, count)

test13 <- test %>%
  filter(year == '2012' & month == 'January') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train13)
# head(test13)

AR24 <- arima(train13$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test13)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test13$count <- round(fcst$mean)
# test13

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train13$count)

```

### February

```{r}


train14 <- train %>%
  filter(year == '2012' & month == 'February') %>%
  select(datetime, count)

test14 <- test %>%
  filter(year == '2012' & month == 'February') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train14)
# head(test14)

AR24 <- arima(train14$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test14)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test14$count <- round(fcst$mean)


RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train14$count)


```


### March

```{r}


train15 <- train %>%
  filter(year == '2012' & month == 'March') %>%
  select(datetime, count)

test15 <- test %>%
  filter(year == '2012' & month == 'March') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train15)
# head(test15)

AR24 <- arima(train15$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test15)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test15$count <- round(fcst$mean)

# test15


RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train15$count)


```


### April

```{r}


train16 <- train %>%
  filter(year == '2012' & month == 'April') %>%
  select(datetime, count)

test16 <- test %>%
  filter(year == '2012' & month == 'April') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train16)
# head(test16)

AR24 <- arima(train16$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test16)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test16$count <- round(fcst$mean)


RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train16$count)


```


### May

```{r}


train17 <- train %>%
  filter(year == '2012' & month == 'May') %>%
  select(datetime, count)

test17 <- test %>%
  filter(year == '2012' & month == 'May') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train17)
# head(test17)

AR24 <- arima(train17$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test17)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test17$count <- round(fcst$mean)

# test5

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train17$count)

```

### June

```{r}


train18 <- train %>%
  filter(year == '2012' & month == 'June') %>%
  select(datetime, count)

test18 <- test %>%
  filter(year == '2012' & month == 'June') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train18)
# head(test18)

AR24 <- arima(train18$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test18)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test18$count <- round(fcst$mean)

# test18

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train18$count)

```

### July

```{r}


train19 <- train %>%
  filter(year == '2012' & month == 'July') %>%
  select(datetime, count)

test19 <- test %>%
  filter(year == '2012' & month == 'July') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train19)
# head(test19)

AR24 <- arima(train19$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test19)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test19$count <- round(fcst$mean)

# test19

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train19$count)

```


### August

```{r}

train20 <- train %>%
  filter(year == '2012' & month == 'August') %>%
  select(datetime, count)

test20 <- test %>%
  filter(year == '2012' & month == 'August') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train20)
# head(test20)

AR24 <- arima(train20$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test20)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test20$count <- round(fcst$mean)

# test20

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train20$count)

```


### September

```{r}

train21 <- train %>%
  filter(year == '2012' & month == 'September') %>%
  select(datetime, count)

test21 <- test %>%
  filter(year == '2012' & month == 'September') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train21)
# head(test21)

AR24 <- arima(train21$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test21)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test21$count <- round(fcst$mean)

# test21

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train21$count)

```


### October

```{r}

train22 <- train %>%
  filter(year == '2012' & month == 'October') %>%
  select(datetime, count)

test22 <- test %>%
  filter(year == '2012' & month == 'October') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train22)
# head(test22)

AR24 <- arima(train22$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test22)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test22$count <- round(fcst$mean)

# test22

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train22$count)

```



### November

```{r}

train23 <- train %>%
  filter(year == '2012' & month == 'November') %>%
  select(datetime, count)

test23 <- test %>%
  filter(year == '2012' & month == 'November') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train23)
# head(test23)

AR24 <- arima(train23$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test23)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test23$count <- round(fcst$mean)

# test23

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train23$count)

```


### December

```{r}

train24 <- train %>%
  filter(year == '2012' & month == 'December') %>%
  select(datetime, count)

test24 <- test %>%
  filter(year == '2012' & month == 'December') %>%
  mutate(count = NA) %>%
  select(datetime, count)

# head(train24)
# head(test24)

AR24 <- arima(train24$count,order=c(25,0,0))
# tsdisplay(residuals(AR24),lag.max=25,main="AR(24) Resid. Diagnostics")

number = nrow(test24)

acf(AR24$residuals)
pacf(AR24$residuals)

checkresiduals(AR24)

fcst <- forecast(AR24, h=number)

autoplot(fcst)

# point estimate (mean)
test24$count <- round(fcst$mean)

# test24

RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train24$count)

```



### Combine all of the individual data frames


```{r warning = FALSE}
combined <- data.frame(datetime=character(),
                 count=double(), 
                 stringsAsFactors=FALSE) 



combined <- bind_rows(test1, test2, test3, test4, test5, test6, test7, test8, test9, test10, test11, test12,
                      test13, test14, test15, test16, test17, test18, test19, test20, test21, test22, test23, test24)

combined <- combined %>%
  mutate(count = floor(ifelse(count < 0, 0, count)))

# write.csv(combined, file = "~/Desktop/ts_kaggle_submission.csv", row.names = F)

```


### RMSLE: Root Mean Squared Logarithmic Error Loss
```{r}

# RMSLE(y_pred = floor(ifelse(fcst$fitted < 0, 0, round(fcst$fitted))), y_true = train2$count)

```


## Submit

```{r}

# Kaggle Score:  RMSLE = 1.33332
score = (1 - (3008 / 3251)) * 100

# We only beat ~7% of all submissions
score

```





